MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-02-12 MAESTROeX_I/paper.tex
add official AMReX citation

We would like to revamp our previous MAESTRO code by moving to the AMReX framework
so that we can take advantage of all of the latest features of the AMReX libraries. 
In addition, we want to modify and simplify the existing numerical scheme 
to both encourage new users and to develop a method that will lend itself more 
easily to incorporating SDC and other high-order methods. 
Irregular base state spacing is considered in order to improve spatial resolution 
that have been seen in the previous MAESTRO code in some test cases.

>>>>

We would like to revamp our previous MAESTRO code by moving to the AMReX \cite{AMReX} framework
so that we can take advantage of all of the latest features of the AMReX libraries. 
In addition, we want to modify and simplify the existing numerical scheme 
to both encourage new users and to develop a method that will lend itself more 
easily to incorporating SDC and other high-order methods. 
Irregular base state spacing is considered in order to improve spatial resolution 
that have been seen in the previous MAESTRO code in some test cases.
